### 2023-02-23 paper.tex
Recreate t5 picture

\documentclass[twoside]{article}
\usepackage{seminarpaper}
\usepackage[backend=bibtex,style=numeric]{biblatex}
\usepackage{csquotes}

@@

@@

\subsection{Text-to-Text Transfer Transformer}

>>>>

\documentclass[twoside]{article}
\usepackage{seminarpaper}
\usepackage[backend=bibtex,style=numeric]{biblatex}
\usepackage{csquotes}
\usepackage{tikz}

\usetikzlibrary{positioning}
\usetikzlibrary{matrix}

@@

TODO: explain why I chose these specific models to look at maybe?

\section{Training}
TODO: write about transfer learning in general, take from bert.
means big pretraining and then using that strong understanding
to fine tune for specific tasks

@@

\subsection{Text-to-Text Transfer Transformer}
\begin{tikzpicture}[line width=0.3mm, align=center, font=\sffamily]
  % Nodes
  \matrix [matrix of nodes, row sep=2mm] (rightmat) {
    \node (translatein) [rounded corners=3pt, draw, fill=green!20] {"translate English to German: That is good."}; \\
    \node (colain)[rounded corners=3pt, draw, fill=red!20] {"cola sentence: The\\course is jumping well."}; \\
    \node (stsbin)[rounded corners=3pt, draw, fill=yellow!20] {"stsb sentence1: The rhino grazed\\on the grass. sentence2: A rhino\\is grazing in a field."}; \\
    \node (summaryin)[rounded corners=3pt, draw, fill=cyan!20] {"summarize: state authorities\\dispatched emergency crews tuesday to\\survey the damage after an onslaught\\of severe weather in mississippi..."}; \\
  };
  \node [right=of rightmat, rounded corners=3pt, draw, fill=gray!20] (t5) {\Huge T5};
  \matrix [matrix of nodes, right=of t5, row sep=2mm] {
    \node (translateout)[rounded corners=3pt, draw, fill=green!20] {"Das ist gut."}; \\
    \node (colaout)[rounded corners=3pt, draw, fill=red!20] {"not acceptable"}; \\
    \node (stsbout)[rounded corners=3pt, draw, fill=yellow!20]  {"3.8"}; \\
    \node (summaryout)[rounded corners=3pt, draw, fill=cyan!20] {"six people hospitalized after\\a storm in attala county."}; \\
  };

  % Lines
  \draw [-] (translatein.east) .. controls +(right:5mm) and +(left:5mm) .. (t5.west);
  \draw [-] (colain.east) .. controls +(right:5mm) and +(left:5mm) .. (t5.west);
  \draw [-] (stsbin.east) .. controls +(right:5mm) and +(left:5mm) .. (t5.west);
  \draw [-] (summaryin.east) .. controls +(right:5mm) and +(left:5mm) .. (t5.west);

  \draw [-] (translateout.west) .. controls +(left:5mm) and +(right:5mm) .. (t5.east);
  \draw [-] (colaout.west) .. controls +(left:5mm) and +(right:5mm) .. (t5.east);
  \draw [-] (stsbout.west) .. controls +(left:5mm) and +(right:5mm) .. (t5.east);
  \draw [-] (summaryout.west) .. controls +(left:5mm) and +(right:5mm) .. (t5.east);
\end{tikzpicture}
